A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Add EGf representation

Assuming standard CTL syntax and semantics, i.e. for the set of atomic
propositions $AP$
\begin{enumerate}
    \item{$p \in AP$ is a CTL formula.}
    \item{
        Given two CTL formulas $f_1$ and $f_2$, also $\neg f_1$, $f_1 \land f_2$,
        $\text{\textbf{EX}} f$,
        $\text{\textbf{E}} \lbrack f_1 \text{\textbf{U}} f_2 \rbrack$ and
        $\text{\textbf{EG}} f_1$ are CTL formulas.
    }
\end{enumerate}

@@

>>>>

Assuming standard CTL syntax and semantics, i.e. for the set of atomic
propositions $AP$
\begin{enumerate}
    \item{$p \in AP$ is a CTL formula.}
    \item{
        Given two CTL formulas $f_1$ and $f_2$, also $\neg f_1$, $f_1 \land f_2$,
        $\text{\textbf{EX}} f_1$,
        $\text{\textbf{E}} \lbrack f_1 \text{\textbf{U}} f_2 \rbrack$ and
        $\text{\textbf{EG}} f_1$ are CTL formulas.
    }
\end{enumerate}

@@

Now, equivalent $\mu$-Calculus relational terms need to be formulated for
$\text{\textbf{EX}} f$,
$\text{\textbf{E}} \lbrack f_1 \text{\textbf{U}} f_2 \rbrack$ and
$\text{\textbf{EG}} f$. A CTL formula $f$ is \textbf{True} at state $s$ iff
$R \left( s \right)$ is \textbf{True}.

$\text{\textbf{EX}} f$ is satisfied for a state $s$ iff a state satisfying $f$
exists and $R \left( s, t \right)$ holds. In terms of $\mu$-Calculus relational
terms, $\text{\textbf{EX}} f$ can be formulated as
$\lambda u \lbrack \exists v \left( f(v) \land R \left( u, v \right) \right) \rbrack$.
